---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Sage Blunt"
date: "8/26/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

( 1846 rows, 3 columns. Variables - dataset, x, y.)

### Exercise 2



Dino Dataset Plot 

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Dino Dataset Correlation

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Star dataset plot

```{r plot-star,fig.height=3, fig.width=6}
      star_data <- datasaurus_dozen %>%
        filter(dataset == "star")

  ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Star dataset correlation

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

The value of r for both the dino data and star data are similar.


### Exercise 4

Circle dataset plot

```{r plot-circle,fig.height=3, fig.width=6}
      circle_data <- datasaurus_dozen %>%
        filter(dataset == "circle")

  ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Circle dataset correlation

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

The value of r for the circle dataset is also very similar to the dino dataset.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)