---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Sage Blunt"
date: "8/26/2019"
output: 
  html_document: 
    fig_height: 6
    fig_width: 8
    highlight: zenburn
    theme: cosmo
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

( 1846 rows, 3 columns. Variables - dataset, x, y.)


### Exercise 2

*Dino Dataset Plot* 
```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

*Dino Dataset Correlation*
```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```


### Exercise 3

*Star Dataset Plot*
```{r plot-star,fig.height=3, fig.width=6}
      star_data <- datasaurus_dozen %>%
        filter(dataset == "star")

  ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

*Star Dataset Correlation*
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

- The value of r for both the dino data and star data are similar.


### Exercise 4

*Circle Dataset Plot*
```{r plot-circle,fig.height=3, fig.width=6}
      circle_data <- datasaurus_dozen %>%
        filter(dataset == "circle")

  ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

*Circle Dataset Correlation*
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

- The value of r for the circle dataset is also very similar to the dino dataset.


### Exercise 5

*Plots for All Datasaurus Datasets*
```{r plot-datasaurus,fig.height=7, fig.width=6}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```


*Correlations for All Datasaurus Datasets*
``` {r corr-datasaurus}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

- All r values are very similar to each other despite their plots being extremely different. This shows how correlation on its own can be decieving.

